Supplementary material

### 2025-11-21 paper/01-introduction.qmd
up antes de borrar tiempo

What is the legitimate extent of market inequality in the eyes of the public? Since the early 1980s, many countries have experienced a widespread retreat from universal welfare programs and a shift toward the privatization and commodification of public goods, welfare policies, and social services [@gingrich_making_2011; @streeck_how_2016]. In Latin America, as elsewhere, neoliberal reforms reshaped welfare-state institutions by extending market logic into domains of social reproduction that were traditionally governed by the state [@ferre_welfare_2023]. This transformation reduced the role of public provision and increased the presence of private actors in core social services [@ferre_welfare_2023]. Echoing Polanyi's [-@polanyi_great_1975] insight that markets constitute a distinct moral order, the institutional diffusion of market rules has fostered a corresponding moral economy: a constellation of norms and values concerning fair allocation, embedded in institutions and shaping individual subjectivities [@mau_inequality_2015; @svallforsMoralEconomyClass2006a]. Within this framework, a growing body of research examines the extent to which, and the mechanisms by which, citizens consider it fair that the allocation of services like health care, pensions, and education be governed by market-based criteria---a phenomenon known as *market justice preferences* [@busemeyer_skills_2014; @immergut_it_2020; @castillo_socialization_2024; @castillo_perceptions_2025; @koos_moral_2019; @lindh_bringing_2023; @lindh_public_2015]. Understanding these preferences is crucial, as they contribute to legitimizing economic inequality by framing it as the fair result of individual responsibility and limited state intervention [@mau_inequality_2015].

Existing literature shows that market justice preferences are shaped by both the economic and institutional context and individuals' positions within social stratification. Grounded in the notion that economic institutions influence people's normative attitudes [@immergut_theoretical_1998], studies find that countries with stronger public provision or more expansive welfare states exhibit lower levels of market justice preferences [@busemeyer_skills_2014; @immergut_it_2020], while more privatized contexts show stronger support for market-based criteria [@castillo_socialization_2024; @lindh_public_2015]. In such contexts, market justice preferences tend to rise as individuals "ascend" the social structure, with those in more privileged positions in terms of class, education, and income holding stronger preferences for market-based solutions compared to those in more disadvantaged or at-risk positions [@lee_fairness_2023; @vondemknesebeck_are_2016; @immergut_it_2020; @castillo_socialization_2024; @otero_power_2024; @lindh_public_2015; @svallfors_political_2007].

Market justice preferences are shaped not only by objective socioeconomic conditions but also by popular beliefs about inequality. Among these, meritocracy is a key normative principle underpinning market-based distributive preferences [@mau_inequality_2015]. Studies show that individuals with stronger meritocratic beliefs tend to perceive less inequality and legitimize it by attributing economic differences to personal achievement [@mijs_paradox_2019; @wilson_role_2003; @batruch_belief_2023]. In highly unequal societies where access to services is largely governed by market logic, such beliefs play a critical role in normalizing inequality. Recent evidence from Chile shows that students who believe effort and talent are rewarded in their country express stronger preferences for market-based access to healthcare, pensions, and education [@castillo_socialization_2024].

Although it is clear that one's social position influences market justice preferences, the question of how upward or downward mobility within the social structure affects these preferences remains unanswered. This question is far from trivial, especially in Latin America, where many have experienced various forms of mobility amid high economic inequality and deep welfare privatization [@lopez-roldan_comparative_2021; @torche_intergenerational_2014; @ferre_welfare_2023]. Social origins and destinations affect attitudes toward inequality in distinct ways [ @jaime-castillo_social_2019; @gugushvili_intergenerational_2016; @day_movin_2017; @gugushvili_subjective_2017; @wen_does_2021; @mijs_belief_2022], while movement between these positions exposes individuals to different experiences and mechanisms that shape their views on what is fair [@gugushvili_trends_2014; @mau_inequality_2015]. Building on this research, examining the effects of social mobility on market justice preferences can help to illuminate how inequalities in access to social services are justified among individuals who have experienced, or not, changes in their social standing, and what are the normative mechanisms that guide this justification [@mau_inequality_2015].

Beyond their isolated effects, social mobility and meritocratic beliefs interact in complex ways to shape market justice preferences. Among others, a key mechanism proposed in the literature to explain how mobility influences distributive justice preferences is the psychological process of self-serving bias in causal attribution [@schmidt_experience_2011; @gugushvili_intergenerational_2016c]. This bias suggests that individuals attribute failures---such as downward mobility---to external factors, while crediting successes---such as upward mobility---to their own merit and effort [@miller_selfserving_1975]. Those who experience upward mobility tend to view their social position as earned, making them more likely to believe that individuals are responsible for their own success or failure. Research shows that upward mobility is associated with weaker preferences for redistribution [@schmidt_experience_2011; @gugushvili_intergenerational_2016c; @jaime-castillo_social_2019; @alesina_intergenerational_2018] and stronger legitimacy of income inequality [@shariff_income_2016]. In contrast, individuals who experience downward mobility tend to blame structural factors like inequality and are more supportive of redistribution while rejecting merit-based explanations [@gugushvili_trends_2014]. Taken together, I argue that meritocratic beliefs may reinforce this self-serving attribution mechanism by legitimizing one's social status as the outcome of personal merit, closely tied to attribution bias.

Against this background, this article pursues two main objectives: first, to analyze the extent to which intergenerational social mobility influences market justice preferences regarding healthcare, pensions, and education; and second, to examine how meritocratic beliefs may moderate this relationship. Building on a theoretical framework that emphasizes how neoliberal transformations---particularly through the privatization and commodification of key areas of social reproduction---have profoundly reshaped processes of subject formation [@mau_inequality_2015], the central argument is that upward mobility increases support for market justice preferences, while downward mobility decreases it. Moreover, meritocratic beliefs are expected to moderate this relationship by reflecting a self-serving attribution bias, whereby individuals justify their social position in terms of personal merit.

This study focuses on Chile, a particularly intriguing case for examining market justice preferences. Despite significant economic growth and poverty reduction, Chile has some of the highest levels of inequality in Latin America and among OECD countries [@chancel_world_2022; @flores_top_2020]. This inequality coexists with short-range upward mobility among lower-class segments moving into middle strata, though strong barriers remain to reaching higher positions [@torche_intergenerational_2014; @espinoza_estratificacion_2013]. What makes Chile especially salient is that much of this inequality is rooted in deep neoliberal reforms that institutionalized the privatization and commodification of key social sectors [@madariaga_three_2020]. Introduced during the dictatorship (1973--1989) and expanded in democracy, these reforms enabled the unprecedented emergence of markets in health, pensions, and education, with provision segmented by individuals' ability to pay and supported by public subsidies [@boccardo_30_2020]. In parallel---and despite waves of protest against inequality and commodification from 2006 to 2019 [@somma_no_2021]---Chilean subjectivities have been increasingly shaped by neoliberal discourses and market logics, influencing their attitudes toward inequality and welfare distribution [@araujo_desafios_2012; @canalesceron_sujeto_2021].

In this context, the questions that guide this research are as follows:

(1) To what extent does intergenerational social mobility influence market justice preferences regarding healthcare, pensions, and education in Chile?
(2) How do meritocratic beliefs condition or moderate this relationship in the Chilean context?

To address these questions, this study draws on large-scale, representative survey data collected in 2018 from the urban Chilean population aged 18 to 75 (n = 2,726). The next section outlines the theoretical framework linking market justice preferences, social mobility, and meritocratic beliefs, and proposes a set of hypotheses. This is followed by a description of the data, variables, and analytical strategy. The final sections present the empirical findings, offer an interpretation of the results, and conclude with a discussion of their implications.

>>>>

What is the legitimate scope of market inequality in the eyes of the public? Since the early 1980s, many countries have experienced a rollback of universal welfare programs and a shift toward the privatisation and commodification of public goods and social services [@gingrich_making_2011; @streeck_how_2016]. In Latin America, these reforms extended market logic into domains of social reproduction long governed by the state, shrinking public provision and expanding private actors in core welfare sectors [@ferre_welfare_2023]. From a moral-economy perspective, this diffusion of market rules has reconfigured the normative order: through policy feedback, welfare institutions increasingly embed market-based criteria of “fair” allocation and shape how citizens understand deservingness and the balance between state and market [@svallforsMoralEconomyClass2006a; @koos_moral_2019]. Against this backdrop, growing scholarship examines *market justice preferences*—the extent to which citizens regard market-based criteria as a fair basis for access to essential services such as healthcare, education and pensions [@castillo_perceptions_2025; @svallfors_political_2007; @lindh_public_2015]. These orientations matter because they help legitimise economic inequality by portraying stratified outcomes as a fair result of individual responsibility and limited state intervention.

This article examines public support for the commodification of pension welfare—specifically, whether people consider it fair that access to better pensions depends on income or contributions. Pension privatisation lies at the core of Latin America’s trajectory of commodification [@huber_political_2000], making pension systems a strategic domain for analysing how market principles become normatively embedded [@mau_inequality_2015]. As many countries expanded mandatory or voluntary individual-capitalisation schemes—most radically in Chile—pensions became organised around contribution-based entitlements and market performance [@arenas_sistemas_2019; @verbic_political_2019]. This shift reshapes not only how pension institutions allocate old-age risk, heightening exposure to poverty in retirement and tying benefit levels to lifetime labour-market trajectories [@oecd_pensions_2023; @madero-cabib_private_2019], but also reshape the justice principles citizens associate with old-age security: people have to judge whether higher benefits should follow market-derived criteria or solidaristic principles [@arrizabalomontoro_debate_2019; @borzutzky_pension_2012]. Although we know something about what people consider a “just” monetary pension [@castillo_deserving_2019] and about support for public versus private provision [@busemeyer_welfare_2020; @jaime-castillo_public_2013], we still lack systematic evidence on how citizens assess the fairness of market-dependent access to pensions.

Research shows that support for market-based access to welfare services is strongly stratified: individuals with higher income, education or class position are more likely to endorse market-based criteria than disadvantaged groups [@busemeyer_skills_2014; @immergut_it_2020;  @lindh_public_2015;  @svallfors_political_2007]. Evidence for pensions points in the same direction: higher income and greater financial gains in funded schemes correlate with stronger support for market-oriented pension policies [@kerner_pension_2020]. Yet we know very little about how movement within the class structure shapes preferences for pension commodification. This gap is especially salient in Latin America, where mobility has unfolded under high inequality and deeply privatised welfare regimes [@lopez-roldan_comparative_2021]. Social origins and destinations anchor material interests and justice principles [@alesina_intergenerational_2018; @langsaether_explaining_2022; @gugushvili_subjective_2017], while movement between these positions exposes individuals to new risks, resources and normative environments that reshape fairness judgements [@gugushvili_trends_2014; @helgason_longterm_2023]. As @mau_inequality_2015 argues, social mobility can foster market-justice orientations, helping explain how inequalities in access to welfare services become normatively sustained.

The literature identifies several mechanisms through which mobility may shape distributive-justice preferences—material self-interest [@benabou_social_2001], socialisation and acculturation [@jaime-castillo_social_2019], learning through long-term exposure [@helgason_longterm_2023], and cognitive attributions such as self-serving bias or privilege awareness [@gugushvili_intergenerational_2016c; @molina_its_2019]. While distinct, these accounts converge in highlighting two broad channels relevant for market-based welfare: shifts in material stakes and shifts in normative frames [@mau_inequality_2015]. In this paper, I do not treat these mechanisms as mediators but use them to guide hypotheses about heterogeneity: if mobility alters preferences through material interests and normative updating, its effects should be most potent among those who interpret social outcomes through merit-based evaluations of effort [@castillo_perceptions_2025; @mijs_belief_2022].

Against this background, this article pursues two aims: first, to assess whether intergenerational mobility causally affects support for the commodification of pensions; and second, to examine whether this effect varies by meritocratic beliefs. I argue that mobility works through two main channels. Upward mobility increases earnings, expected returns in a funded system and perceived economic security, making contribution-based access more appealing. At the same time, integration into higher-class networks exposes people to more individualistic norms and effort-based understandings of fairness. Downward mobility, in turn, heightens economic insecurity, dependence on collective protection and attachment to solidaristic principles, lowering support for market allocation. Meritocratic beliefs are conceptualised not as mediators but as moderators. Among those who see mobility as a fair reward for effort, both material and normative effects should be amplified, producing higher support for pension commodification. The paper contributes to research on market justice by focusing on a specific welfare domain and by providing causal evidence on how mobility shapes distributive preferences.

This study focuses on Chile, a particularly instructive case for examining preferences for pension commodification. Despite sustained economic growth, Chile combines high and persistent inequality with short-range upward mobility and substantial barriers to higher-class positions [@flores_top_2020; @salgado_uplifting_2025; @torche_intergenerational_2014]. It was the first country worldwide to fully replace a public pay-as-you-go system with a mandatory, privately administered (through pension fund administrators, AFPs) defined-contribution scheme, while the state has progressively expanded a segmented solidarity pillar to compensate for insufficient benefits [@madariaga_three_2020; @boccardo_30_2020; @solimano_rise_2021]. In parallel—and despite waves of protest from 2006 to 2019 targeting the AFP system [@somma_no_2021]—Chilean subjectivities have been increasingly shaped by neoliberal discourses and market logics, influencing attitudes toward pension distribution and inequality [@araujo_desafios_2012; @galvez_con_2023]. The combination of profound inequality, market-driven old-age security and contested legitimacy makes Chile a critical case for analysing how mobility and meritocratic beliefs structure support for pension commodification.

To address these questions, the study draws on large-scale, representative survey data for the urban Chilean population collected in 2016, 2018 and 2023. It adopts a causal framework of mobility effects inspired by @breen_effects_2024. The following section outlines the theoretical framework linking preferences for market-based welfare, social mobility and expected heterogeneity by meritocratic beliefs and time, and derives hypotheses. A subsequent section presents the causal identification strategy, the data, the variables, and the analytical approach. The empirical sections report the findings and interpret their implications. The article concludes by discussing what these results reveal about the politics of market-based pension welfare and social mobility.

### 2025-11-21 paper/04-analysis.qmd
up antes de borrar tiempo

```{r}
#| label: fig-interact
#| fig-cap: "Effects of intergenerational occupational mobility on preferences for pension commodification, by meritocratic perception. Coefficient plot of origin-specific ATT estimates comparing mobility versus immobility, estimated from interaction models (T × Merit). Points show simple slopes of the mobility effect at low merit and high merit; bars are 95% confidence intervals. Estimates from pooled WLS with doubly robust adjustment, wave fixed effects, and standard errors clustered by individual."
#| out-width: '90%'
#| fig-asp: 0.8
#| fig-cap-location: bottom
#| echo: false
#| results: asis

@@

@fig-interact shows that neither the interaction terms nor the mobility coefficients reach conventional significance across trajectories, indicating no detectable moderation of the causal mobility effect by meritocratic perceptions at the 95% level. Directionally, in the left panel, the interaction is positive for Middle→High ($\beta$ = 0.15, 95% CI [−0.03, 0.33]) and Low→High ($\beta$ = 0.05, [−0.14, 0.24]), suggesting, if anything, somewhat larger pro-commodification effects among high-merit respondents when upwardly mobile, whereas it is negative for High→Low ($\beta$ = −0.14, [−0.38, 0.10]) and High→Middle ($\beta$ = −0.03, [−0.23, 0.17]), showing weaker pro-commodification effects under downward mobility at high merit. Focusing on the treatment effect at low meritocracy (the reference category) at the right panel, the mobility coefficient captures the origin-specific ATT comparing movers to their immobility counterfactual among low-merit respondents. These effects are small and imprecise across trajectories: Low→Middle ($\beta$ = −0.02, [−0.09, 0.04]) and Low→High ($\beta$ = −0.03, [−0.10, 0.05]) are near zero. Middle→High is positive but not significant ($\beta$ = 0.07, [−0.01, 0.14]), Middle→Low is null ($\beta$ = -0.00, [−0.07, 0.06]), and downward from high shows negative, borderline estimates: High→Middle ($\beta$ = −0.07, [−0.15, 0.00]) and High→Low ($\beta$ = −0.08, [−0.15, 0.00]). Substantively, I do not find evidence that meritocratic perceptions moderate the causal effect of mobility, although the signs align with the idea that upward mobility at high merit tilts attitudes toward commodification, and downward mobility at high merit tilts them away.

```{r}
#| label: tbl-inttime
#| tbl-cap: "Effects of intergenerational occupational mobility on preferences for pension commodification, by survey wave"
#| tbl-cap-location: top
#| results: asis
#| echo: false

ccoef <- list(
  "(Intercept)" = "Intercept",
  "t" = "Mobility treatment",
  "ola2018" = "Wave 2018",
  "ola2023" = "Wave 2023",
  "t:ola2018" = "Mobility treatment x Wave 2018",
  "t:ola2023" = "Mobility treatment x Wave 2023"
  )

texreg::texreg(list(mp_lm_t,
               mp_lh_t,
               mp_mh_t,               
               mp_ml_t,
               mp_hm_t,
               mp_hl_t),
          custom.model.names = c(
            "Low-Middle",
            "Low-High",
            "Middle-High",            
            "Middle-Low",
            "High-Middle",
            "High-Low"
          ),   caption.above = NULL,
               caption = NULL,
               custom.coef.map = ccoef,
               digits = 2,
               groups = list("Wave (Ref.= 2016)" = 3:4, "Mobility treatment x Wave (Ref.= 2016)" = 5:6),
               custom.note = "Note: Cells contain regression coefficients with confidence intervals in parentheses. %stars.",
               leading.zero = T,
               use.packages = F,
               booktabs = F,
               scalebox = 0.80,
               center = T,float.pos = "H!",
               custom.gof.rows = list("Controls"=rep("Yes",6)))

@tbl-inttime shows the causal heterogeneity of the mobility effect across the different waves of the survey. Regarding temporal heterogeneity, the only statistically significant interaction term is observed for the High→Middle trajectory in 2023 ($\beta_{\text{int}} = 0.19$), 95% CI [0.01, 0.38]). However, when this interaction is added to the baseline effect in 2016 (-0.19), the marginal effect of High→Middle mobility in 2023 is approximately zero, and its confidence interval includes the null. Thus, rather than indicating a reversal toward a positive effect, the evidence suggests that the negative impact of downward mobility from high backgrounds is confined to 2016 and attenuates over time. No comparable temporal changes are observed in the remaining trajectories. Overall, the results provide little support for strong time-conditional heterogeneity in mobility effects, beyond the fading of the initially negative High→Middle effect.

>>>>

```{r}
#| label: fig-interact
#| fig-cap: "Effects of intergenerational occupational mobility on preferences for pension commodification, by meritocratic perception. Coefficient plot of origin-specific ATT estimates comparing mobility versus immobility, estimated from interaction models (T × Merit). Points show the marginal effects (simple slopes) of the mobility treatment at low and high merit; bars are 95% confidence intervals. Estimates from pooled WLS with doubly robust adjustment, wave fixed effects, and standard errors clustered by individual."
#| out-width: '90%'
#| fig-asp: 0.8
#| fig-cap-location: bottom
#| echo: false
#| results: asis

@@

@fig-interact displays the origin-specific ATT estimates from the meritocracy interaction models as marginal effects of the mobility treatment at low and high meritocratic beliefs. For low-merit respondents, mobility effects are uniformly small and imprecise across trajectories: Low→Middle ($\beta$ = −0.02, 95% CI [−0.09, 0.04]), Low→High ($\beta$ = −0.03, [−0.10, 0.05]), Middle→Low ($\beta$ = −0.00, [−0.07, 0.06]), and a modest, non-significant positive estimate for Middle→High ($\beta$ = 0.07, [−0.01, 0.14]), while downward moves from high origin show borderline negative effects (High→Middle: $\beta$ = −0.07, [−0.15, 0.00]; High→Low: $\beta$ = −0.08, [−0.15, 0.00]). Among high-merit respondents, the pattern is directionally consistent with meritocratic moderation but statistically robust only for one trajectory: the ATT for Middle→High at high merit is positive and significant ($\beta$ = 0.22, [0.05, 0.38]), whereas Low→Middle ($\beta$ = 0.02, [−0.13, 0.16]), Low→High ($\beta$ = 0.02, [−0.15, 0.20]), High→Middle ($\beta$ = −0.10, [−0.28, 0.09]), and High→Low ($\beta$ = −0.22, [−0.44, 0.00]) remain statistically indistinguishable from zero. Overall, these results provide only limited and trajectory-specific evidence that meritocratic beliefs moderate the causal effect of intergenerational occupational mobility on preferences for pension commodification, with a clearer pro-commodification sign only for upward mobility from middle to high status among high-merit respondents.

```{r}
#| label: fig-interact-wave
#| fig-cap: "Effects of intergenerational occupational mobility on preferences for pension commodification, by survey wave. Coefficient plot of origin-specific ATT estimates comparing mobility versus immobility, estimated from interaction models (T × Wave). Points show the marginal effects (simple slopes) of the mobility treatment in 2016, 2018, and 2023; bars are 95% confidence intervals. Estimates from pooled WLS with doubly robust adjustment, wave fixed effects, and standard errors clustered by individual."
#| out-width: '90%'
#| fig-asp: 0.8
#| fig-cap-location: bottom
#| echo: false
#| results: asis

g5+
  theme(legend.text = element_text(size = 10))
```

I find no consistent evidence of heterogeneous causal effects across survey waves. @fig-interact-wave displays the marginal effects of mobility trajectories on market-justice preferences for pensions in 2016, 2018, and 2023. Across trajectories, the estimated ATTs remain small and their confidence intervals largely overlap over time. Upward mobility from middle origin shows a positive and statistically significant effect in 2016 (Middle→High, $\beta$ = 0.13, 95% CI [0.05, 0.22]) and downward mobility from high origin displays negative effects at baseline (High→Middle and High→Low, both $\beta$ ≈ −0.19, CIs excluding zero), but these patterns attenuate and become statistically indistinguishable from zero by 2023. Taken together, the results suggest that any initial pro-commodification response to upward mobility and de-commodifying response to downward mobility are not stable over time, and the causal effect of mobility on preferences for pension commodification is effectively time-invariant over the 2016–2023 period.

### 2025-11-21 paper/07-supplementary-material.qmd
up antes de borrar tiempo

```{r}
#| label: tbl-complete3
#| tbl-cap: "Interactions effects between intergenerational occupational mobility and perceived meritocracy on preferences for pension commodification, with covariates and wave fixed effects."
#| tbl-cap-location: top
#| results: asis
#| echo: false

ccoef <- list(
  "(Intercept)" = "Intercept",
  "t" = "Mobility treatment",
  "mHigh" = "High meritocracy perception (Ref.= Low)",
  "t:mHigh" = "Mobility treatment x High meritocracy perception (Ref.= Low)"
)

texreg(list(mp_lm_i,
               mp_lh_i,
               mp_mh_i,
               mp_ml_i,
               mp_hm_i,
               mp_hl_i),
          custom.model.names = c(
            "Low-Middle",
            "Low-High",
            "Middle-High",
            "Middle-Low",
            "High-Middle",
            "High-Low"
          ),
          caption.above = NULL,
          caption = NULL,
          custom.coef.map = ccoef,
          digits = 2,
          custom.note = "Note: Cells contain regression coefficients with confidence intervals in parentheses. %stars.",
          leading.zero = T,
          use.packages = F,
          booktabs = F,
          scalebox = 0.7,
          center = T,float.pos = "H!",
          custom.gof.rows = list("Controls"=rep("Yes",6)))

>>>>

```{r}
#| label: tbl-complete3
#| tbl-cap: "Marginal effects of mobility by meritocratic perception (Low vs High Meritocracy)."
#| tbl-cap-location: top
#| results: asis
#| echo: false

df_tab <- df_pension_lab_i %>%
  mutate(
    Trajectory = sub("\\n.*", "", name),
    Merit = term,
    Estimate = round(estimate, 3),
    `Std. Error` = round(std.error, 3),
    `CI Low` = round(conf.low, 3),
    `CI High` = round(conf.high, 3),
  ) %>%
  select(Trajectory, Merit, Estimate, `Std. Error`, `CI Low`, `CI High`)

kableExtra::kable(df_tab,
      format = table_format,
      caption = NULL,
      align = "lcccccc") %>%
kableExtra::kable_classic(full_width = F, html_font = "Cambria")
```

```{r}
#| label: tbl-complete4
#| tbl-cap: "Marginal effects of mobility by survey wave (2016, 2018, and 2023)."
#| tbl-cap-location: top
#| results: asis
#| echo: false

df_tab <- df_pension_lab_t %>%
  mutate(
    Trajectory = sub("\\n.*", "", name),
    Wave = term,
    Estimate = round(estimate, 3),
    `Std. Error` = round(std.error, 3),
    `CI Low` = round(conf.low, 3),
    `CI High` = round(conf.high, 3),
  ) %>%
  select(Trajectory, Wave, Estimate, `Std. Error`, `CI Low`, `CI High`)

kableExtra::kable(df_tab,
      format = table_format,
      caption = NULL,
      align = "lcccccc") %>%
  kableExtra::kable_classic(full_width = F, html_font = "Cambria")
